### 2016-08-18 README.Rmd
fix up ready
fix appveyor badge, update plots

<!-- add a TravisCI badge -->
<!-- Add an appVeyor badge -->
[![Travis-CI Build Status](https://travis-ci.org/njtierney/visdat.svg?branch=master)](https://travis-ci.org/njtierney/visdat) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/tierneyn/visdat?branch=master&svg=true)](https://ci.appveyor.com/project/njtierney/visdat)

@@

by default, `vis_dat` sorts the columns according to the type of the data in the vectors. You can turn this off by setting `sort_type == FALSE`. This feature is better illustrated using the `example2` dataset, borrowed from csv-fingerprint.

@@

vis_dat(example2)

vis_dat(example2, 
        sort_type = FALSE)

@@

The plot above tells us that R reads this dataset as having numeric and integer values, along with some missing data in `Ozone` and `Solar.R`.

@@

@@

vis_dat(example2) %>% ggplotly()

>>>>

<!-- add a TravisCI badge -->
<!-- Add an appVeyor badge -->
[![Travis-CI Build Status](https://travis-ci.org/njtierney/visdat.svg?branch=master)](https://travis-ci.org/njtierney/visdat) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/njtierney/visdat?branch=master&svg=true)](https://ci.appveyor.com/project/njtierney/visdat)

@@

by default, `vis_dat` sorts the columns according to the type of the data in the vectors. You can turn this off by setting `sort_type == FALSE`. This feature is better illustrated using the `airquality` dataset from base R.

@@

vis_dat(airquality, 
        sort_type = FALSE)

@@

The plot above tells us that R reads this dataset as having characters, and integer values, along with some missing data in `Ozone` and `Solar.R`.

### with different data

To demonstrate what visdat looks like when you have different kinds of data, we can look at the `typical_data` from within visdat, created using the excellent [`wakefield package`](https://github.com/trinker/wakefield).

vis_dat(typical_data)

We can also look into using even wider data, looking at `typical_larger_data`

vis_dat(typical_larger_data)

@@

## using `vis_compare`

Sometimes you want to see what has changed in your data. `vis_compare` helps with that. It is currently only just barely working, so keep in mind that this is very much in its beta stages.

For the sake of simplicity, lets make some changes to `iris`, and compare this new dataset

iris_diff <- iris
iris_diff[sample(1:150, 30),sample(1:4, 2)] <- NA

vis_compare(iris_diff, iris)

Here the differences are marked in red.

If you try and compare differences when the dimensions are different, you get an ugly error.

iris_diff_2 <- iris
iris_diff_2$new_col <- iris$Sepal.Length + iris$Sepal.Width

# vis_compare(iris, iris_diff_2)

@@

vis_dat(airquality) %>% ggplotly()
